\documentclass[a4paper]{article}

\usepackage[fancy]{template}
\usepackage{survival-pack}

\setup{%
  subject={Master Project},%
  assignment={Project Description},%
  date={October 19, 2013.}%
}
\setupLocation[short=DIKU]{Datalogisk institut, Copenhagen University}
\setupAuthor[addendum={\email{oleks@diku.dk}}]{Oleksandr Shturmov}

\begin{document}

\maketitle
\thispagestyle{first} % no fancy header on first page (just a fancy footer).

A first past the post (FPTP) election is won by the candidate(s) obtaining a
majority of the votes. The majority may be relative (most votes) or absolute
($> 50\%$). In case of ties, or lack of winners, runoff elections may be held
until a single winner is attained. A voter may vote for exactly one candidate,
typically in an anonymous manner.

FPTP is most common in states that descended from the British and French
empires, e.g. UK, United States, Canada, or India. It is the second most widely
used election system in the world, after party-list proportional representation
(PLPR). FPTP is often used for head of state elections, while PLPR is often
used for parliamentary elections. FPTP can also be used for parliamentary
elections, having single-member elective districts.

Once the votes have been cast, a mission critical process is necessary to count
the votes. This is done by a tally system. The purpose of this project is to
design an open source, automated tally system for FPTP elections, formally
specified using Z notation, implemented and verified in SPARK. This is further
elaborated upon below.

\input{formal-methods}

\input{z-notation}

\input{spark}

\input{learning-objectives}

\input{references}

\end{document}

